---
title: "Sentimental Analysis of Tolstoy"
author: "Alex Salem"
date: "June 17, 2018"
output: xaringan::moon_reader
---

#Introduction
Goal: Create a graph showing sentiment analysis of three Tolstoy novels over his career.
  - I.e., evaluate the relative *positivity* and *negativity* of words in Tolstoy's novels
  
Inspired by Julia Silge's [sentiment analysis of Jane Austen novels](https://juliasilge.com/blog/life-changing-magic/).

Hypothesis: Tolstoy's last novel, *Resurrection*, will have a different sentiment pattern than his others.

---
#Description of the Data
Full text of three novels by Leo Tolstoy:
  - *Childhood* (1852), translated into English by C.J. Hogarth
  - *Anna Karenina* (1877), translated into English by Constance Garnett
  - *Resurrection* (1899), translated into English by Mrs. Louise Maude

Plaintext copies pulled from [Project Gutenburg.](http://www.gutenberg.org/)

Data cleaned and processed using `Python`, then read into R:
```{r, message=FALSE, echo = FALSE}
library(readr)
library(tidytext)
library(tidyverse)
library(viridis)
```
```{r, echo = FALSE}
anna_karenina<- read_csv("anna_karenina.csv", col_types = cols(title = col_factor(levels = NULL)))
childhood <- read_csv("childhood.csv", col_types = cols(title = col_factor(levels = NULL)))
resurrection<- read_csv("resurrection.csv", col_types = cols(title = col_factor(levels = NULL)))
```

```{r, echo = FALSE}
anna_karenina <- anna_karenina %>% 
  rownames_to_column()

childhood <- childhood %>% 
  rownames_to_column()

resurrection <- resurrection %>% 
  rownames_to_column()

```

```{r, message = FALSE, warning = FALSE, echo = FALSE}
data <- bind_rows(childhood, anna_karenina, resurrection)
```

```{r}
glimpse(data)
```

---
#Description of the Data
This data was then combined with the `tidytext::get_sentiments()` function, which has an assignment of sentiment values to words:

```{r}
glimpse(get_sentiments("bing"))
```

---
#Methods
Combined the text data with the sentiment data as follows:
```{r, echo = FALSE}
data_final<- data %>% 
  group_by(title) %>% 
  inner_join(get_sentiments("bing"), by = c("words" = "word")) %>% 
  count(title, index = as.numeric(rowname)%/%max(as.numeric(rowname)/40), sentiment) %>%
  filter(as.numeric(index)!=40) %>% 
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive/(positive+negative))

data_final$title<- fct_relevel(data_final$title, "childhood")
```
- Join sentiment values (either "positive" or "negative") to words in `data`
- Divide each novel's data into 40 sections, then count number of positive and negative words in each section 
- Calculate the ratio of positive words to positive and negative words
```{r}
head(data_final)
```

```{r, echo = FALSE}
labels <- c(childhood = "Childhood, 1852", anna_karenina = "Anna Karenina, 1877", resurrection = "Resurrection, 1899")

plot <- ggplot(data_final, aes(index, sentiment, color =  title)) +
  geom_point(size = .8, show.legend = FALSE) +
  geom_hline(aes(yintercept=.5))+
  geom_segment(aes(x=index, xend = index, y = sentiment, yend = .5)) +
  facet_wrap(~title, ncol = 3, labeller = labeller(title = labels)) +
  ggtitle("Positive and Negative Sentiment in Tolstoy Novels across Plot Trajectory", subtitle = "Sentiment Ratio = Positive Words / (Positive Words + Negative Words) \nSentiment Ratio > 0.5 indicates more positive than negative words \nSentiment Ratio < 0.5 indicates more negative than positive words      ") +
  labs(x = "Plot Trajectory", y = "Sentiment Ratio")+
  expand_limits(y=c(0,1)) +
  scale_color_viridis(discrete = TRUE, name = "Book", labels = labels) +
  theme_minimal() +
  theme(strip.text = element_text(face = "italic")) +
  theme(axis.ticks.x=element_blank()) +
  theme(axis.text.x=element_blank()) +
  theme(legend.position = "bottom")

```

---
#Final Visualization: Lollipop Plot
```{r, echo = FALSE}
plot
``` 

---
#Methods
- Use `geom_point()`, `geom_hline()`, and `geom_segment` to create the lollipops
- `facet_wrap()` by title, relabel with nice names
- Add axis labels and title/subtitle, change colors and legend

--

```{r}
labels <- c(childhood = "Childhood, 1852", anna_karenina = "Anna Karenina, 1877", resurrection = "Resurrection, 1899")

plot <- ggplot(data_final, aes(index, sentiment, color =  title)) +
  geom_point(size = .8, show.legend = FALSE) +
  geom_hline(aes(yintercept=.5))+
  geom_segment(aes(x=index, xend = index, y = sentiment, yend = .5)) +
  facet_wrap(~title, ncol = 3, labeller = labeller(title = labels)) +
  ggtitle("Positive and Negative Sentiment in Tolstoy Novels across Plot Trajectory", subtitle = "Sentiment Ratio = Positive Words / (Positive Words + Negative Words) \nSentiment Ratio > 0.5 indicates more positive than negative words \nSentiment Ratio < 0.5 indicates more negative than positive words      ") +
  labs(x = "Plot Trajectory", y = "Sentiment Ratio")+
  expand_limits(y=c(0,1)) +
  scale_color_viridis(discrete = TRUE, name = "Book", labels = labels) +
  theme_minimal() +
  theme(strip.text = element_text(face = "italic")) +
  theme(axis.ticks.x=element_blank()) +
  theme(axis.text.x=element_blank()) +
  theme(legend.position = "bottom")

```

---
#References
https://machinelearningmastery.com/clean-text-machine-learning-python/

https://www.tidytextmining.com/sentiment.html

https://juliasilge.com/blog/life-changing-magic/

https://python-graph-gallery.com/lollipop-plot/

---
class: center, middle
#Thank you!