---
title: "A Sentimental Analysis of Tolstoy"
author: "Alex Salem"
date: "June 18, 2018"
output: html_document
---
##Introduction
Goal: Create a graph showing sentiment analysis of three Tolstoy novels over his career.

Inspired by Julia Silge's [sentiment analysis of Jane Austen novels](https://juliasilge.com/blog/life-changing-magic/).

Hypothesis: Tolstoy's last novel, *Resurrection*, will have a different sentiment pattern than his others.

##Description of the Data
Full text of three novels by Leo Tolstoy:

- *Childhood* (1852), translated into English by C.J. Hogarth
- *Anna Karenina* (1877), translated into English by Constance Garnett
- *Resurrection* (1899), translated into English by Mrs. Louise Maude

Plaintext copies pulled from [Project Gutenburg.](http://www.gutenberg.org/)

Data cleaned and processed using `Python`:
```{python, eval = FALSE, python.reticulate = FALSE}
import csv
from nltk import word_tokenize

def clean(infilename, outfilename):
	title = outfilename[:-4]
	with open(infilename, "r") as f:
		text = f.read()

	tokens = word_tokenize(text)
	tokens = [w.lower() for w in tokens]
	print(tokens[:100])
	words = [word for word in tokens if word.isalpha()]
	print(words[:100])

	with open(outfilename, "w") as csvfile:
		writer = csv.writer(csvfile)
		writer.writerow(["title", "words"])
		for word in words:
			writer.writerow([title, word])

names = [["anna_karenina_clean.txt", "anna_karenina.csv"], ["boyhood_clean.txt", "boyhood.csv"], 
		["childhood_clean.txt", "childhood.csv"], ["cossacks_clean.txt", "cossacks.csv"],
		["resurrection_clean.txt", "resurrection.csv"], ["war_and_peace_clean.txt", "war_and_peace.csv"],
		["youth_clean.txt", "youth.csv"]]

for name in names:
	clean(name[0], name[1])
```
Then read into R.

Used the following libraries:
```{r, message=FALSE}
library(readr)
library(tidytext)
library(tidyverse)
library(viridis)
```

Then read in the csvs:
```{r}
anna_karenina<- read_csv("anna_karenina.csv", col_types = cols(title = col_factor(levels = NULL)))
childhood <- read_csv("childhood.csv", col_types = cols(title = col_factor(levels = NULL)))
resurrection<- read_csv("resurrection.csv", col_types = cols(title = col_factor(levels = NULL)))
```

Added a column with the row number of each word:
```{r}
anna_karenina <- anna_karenina %>% 
  rownames_to_column()

childhood <- childhood %>% 
  rownames_to_column()

resurrection <- resurrection %>% 
  rownames_to_column()

```

Then, combined rows into one data frame:
```{r, message = FALSE, warning = FALSE}
data <- bind_rows(childhood, anna_karenina, resurrection)
```

```{r}
glimpse(data)
head(data)
```

The `tidytext::get_sentiments()` function assigns sentiment values to words:

```{r}
glimpse(get_sentiments("bing"))
```

##First Visualization
Creating the data frame:
```{r}
bad_data <- data %>% 
  inner_join(get_sentiments("bing"), by = c("words" = "word")) %>%
  count(title, index = as.numeric(rowname)%/%2000, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)

bad_plot<- ggplot(bad_data, aes(index, sentiment, fill = title)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  facet_wrap(~title, ncol = 3, scales = "free_x")
```
* Join sentiment values (either "positive" or "negative") to words in `data`
* Count number of positive and negative words, per 2000 words
* Calculate the difference between those counts, per 2000 words

```{r}
head(bad_data)
```
```{r}
bad_plot
```


##Description of the Data
```{r, results="hide"}
data_final<- data %>% 
  group_by(title) %>% 
  inner_join(get_sentiments("bing"), by = c("words" = "word")) %>% 
  count(title, index = as.numeric(rowname)%/%max(as.numeric(rowname)/40), sentiment) %>%
  filter(as.numeric(index)!=40) %>% 
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive/(positive+negative))

data_final$title<- fct_relevel(data_final$title, "childhood")
```
- Join sentiment values (either "positive" or "negative") to words in `data`
- Divide data into 40 sections, count number of positive and negative words in each section
- Calculate the ratio of positive words to positive and negative words

```{r}
head(data_final)
```


##Methods
- Use `fct_relevel()` (above) to order the books to be facetted by year
- Use `geom_point()`, `geom_hline()`, and `geom_segment()` to create the lollipops
- `facet_wrap()` by title, relabel with nice names
- Add axis labels and title/subtitle
- Change colors and legend
```{r}
labels <- c(childhood = "Childhood, 1852", anna_karenina = "Anna Karenina, 1877", resurrection = "Resurrection, 1899")

plot <- ggplot(data_final, aes(index, sentiment, color =  title)) +
  geom_point(size = .8, show.legend = FALSE) +
  geom_hline(aes(yintercept=.5))+
  geom_segment(aes(x=index, xend = index, y = sentiment, yend = .5)) +
  facet_wrap(~title, ncol = 3, labeller = labeller(title = labels)) +
  ggtitle("Positive and Negative Sentiment in Tolstoy Novels across Plot Trajectory", subtitle = "Sentiment Ratio = Positive Words / (Positive Words + Negative Words) \nSentiment Ratio > 0.5 indicates more positive than negative words \nSentiment Ratio < 0.5 indicates more negative than positive words      ") +
  labs(x = "Plot Trajectory", y = "Sentiment Ratio")+
  expand_limits(y=c(0,1)) +
  scale_color_viridis(discrete = TRUE, name = "Book", labels = labels) +
  theme_minimal() +
  theme(strip.text = element_text(face = "italic")) +
  theme(axis.ticks.x=element_blank()) +
  theme(axis.text.x=element_blank()) +
  theme(legend.position = "bottom")

```

##The plot
```{r}
plot
``` 


##Audience Description
I am aiming for a general audience--but hopefully readers of Tolstoy. :)

##Graph Type Description
This graph is a *lollipop plot*. A lollipop plot is a hybrid of a *scatter plot* and a *bar chart*. 

It shows the relationship between a numeric variable and a categorical or numeric variable. It can also be used to highlight the distace from a certain value--here 0.5, indicating an equal number of positive and negative words.

##Representation Description
This plot shows the relationship between Sentiment Ratio and Plot Trajectory across three Tolstoy novels.

We can use this to get a sense of the "positivity" and "negativity" in Tolstoy's novels over his career. In particular, we can see that *Childhood* and *Anna Karenina* are overall more positive than *Resurrection*.

##How to read it & what to look for
* Start by reading the title and x- and y- axes
* Then look for the baseline value the lollipops are extending from--here 0.5
* Look at one lollipop, interpret the meaning of that point
* Finally, analyze the general shape of the graph

##Presentation Description
Color is used here to distinguish between the three novels.

Additionally, the three novels are arranged by *year* the novel was written, with his earliest novel on the left, and his last novel on the right.


##References
https://machinelearningmastery.com/clean-text-machine-learning-python/

https://www.tidytextmining.com/sentiment.html

https://juliasilge.com/blog/life-changing-magic/

https://python-graph-gallery.com/lollipop-plot/

