---
title: "Tolstoy Brief"
author: "Alex Salem"
date: "June 15, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##Loading libraries:
```{r}
library(readr)
library(tidytext)
library(tidyverse)
```

##Reading in data:
```{r}
anna_karenina<- read_csv("anna_karenina.csv", col_types = cols(title = col_factor(levels = NULL)))
boyhood <- read_csv("boyhood.csv", col_types = cols(title = col_factor(levels = NULL)))
childhood <- read_csv("childhood.csv", col_types = cols(title = col_factor(levels = NULL)))
cossacks <- read_csv("cossacks.csv", col_types = cols(title = col_factor(levels = NULL)))
resurrection<- read_csv("resurrection.csv", col_types = cols(title = col_factor(levels = NULL)))
war_and_peace<- read_csv("war_and_peace.csv", col_types = cols(title = col_factor(levels = NULL)))
youth<- read_csv("youth.csv", col_types = cols(title = col_factor(levels = NULL)))

anna_karenina <- anna_karenina %>% 
  rownames_to_column()

boyhood <- boyhood %>% 
  rownames_to_column()

childhood <- childhood %>% 
  rownames_to_column()

cossacks <- cossacks %>% 
  rownames_to_column()

resurrection <- resurrection %>% 
  rownames_to_column()

war_and_peace <- war_and_peace %>% 
  rownames_to_column()

youth <- youth %>% 
  rownames_to_column()

